Exploring the Presidents Corpus

### 2019-10-23 Source/Paper 1 - Presidents Corpus Paper/PresidentsCorpus.tex
updated Presidents Corpus
updated Pres Paper

This study replicates the research of Berisha and Liss and extends this by adding Donald Trump (DJT) as an additional comparison to RR. This study aims to contribute to our understanding of the pre-diagnosis phase of Alzheimer's Disease and it's effect on language. Our hypothesis is that there will be features of RR's language which change more noticably over time when compared with the two closest appropriate controls. Compared to the previous research study, we explored a wider range of language features within this dataset. In addition, our assumption was that any language deterioration found would be non-linear and so we will be looking at non linear and linear correlations within the data were looked at to see if language decline is constant over time

@@

\begin{figure}[b]
	\centering
	\begin{minipage}[b]{0.4\textwidth}
		\includegraphics[width=150px, height=150px,  natwidth=300, natheight=300]{RRppronLM.jpg}
		\caption{RR Personal Pronouns - Linear Model}
	\end{minipage}

	\begin{minipage}[b]{0.4\textwidth}
		\includegraphics[width=150px, height=150px, natwidth=300, natheight=300]{RRppronLOESS.jpg}
		\caption{RR Personal Pronouns - Local Regression Model}
	\end{minipage}		
\end{figure}

@@

\bibliographystyle{apalike}
\bibliography{main3}

>>>>

Berisha and Liss have developed some very interesting ideas about how we might track changes over time in various lexical features which have been associated with the development of Alzheimer's Disease. We refine these ideas with the aim of exploring the potential for a protocol that can be used for analyzing language deterioration. This study extends the work of Berisha and Liss in a number of ways. Our hypotheses are:
\begin{enumerate}
	\item Language use of RR will be significantly different to our controls (GHWB, DJT).
	\item Additional lexical features will illustrate significant cognitive decline in RR.
	\item Correlations of lexical features over time will be a significantly improved using non-linear models compared to linear models.
\end{enumerate}

@@

\begin{figure}
	\centering
	\begin{minipage}[b]{.45\textwidth}
		\includegraphics[width=6cm, height=5cm]{comp1.png}
	\end{minipage}
	\hfill
		\begin{minipage}[b]{.45\textwidth}
		\includegraphics[width=6cm, height=5cm]{comp2.png}
	\end{minipage}
\end{figure}

@@

\bibliographystyle{ieeetr}
\bibliography{main3}
